API design for machine learning software: experiences from the scikit-learn project

### 2013-06-22 paper.tex
model selection: emphasize generalization performance

As introduced in Section~\ref{sec:estimators}, hyper-parameters set in the
constructor of an estimator determine its behavior. In particular, depending on
the problem, some hyper-parameters produce estimators that are better than
others. The problem of \textit{model selection} is therefore to find, within
some hyper-parameter space, the best combination of hyper-parameters, with
respect to some user-chosen criterion. For example, in the case of a decision
tree, too small values of the \texttt{max\_depth} parameter will make the tree
underfit while too large values will make the tree overfit the training data.
The problem is therefore to find the best trade-off in order to maximize
the performance of the tree on unseen data.

>>>>

As introduced in Section~\ref{sec:estimators}, hyper-parameters set in the
constructor of an estimator
determine the behavior of its learning algorithm
and hence the performance of the resulting model on unseen data.
The problem of \textit{model selection} is therefore to find, within
some hyper-parameter space, the best combination of hyper-parameters, with
respect to some user-chosen criterion. For example, in the case of a decision
tree, too small values of the \texttt{max\_depth} parameter will make the tree
underfit, while too large values will make it overfit.
